### 2015-11-12 AssignmentV/Assignment5-Ditz_Schroeder-WS15-16.tex
ein paar layout und typo verbesserungen

\subsection*{solution if t=s=1}
Generally we only used integers in this task. The constraint for the algortihm are as following if t and s value is 1 now:

@@

In the next step we started to compute each line of the tuple. Starting with constraint \ref{con3} under the aspect of constraint \ref{con5}. All possible tuples respectivly to both constraints from the assignment are:\\
$temp1=\{(0,7);(1,6);(2,5);(3,4);(4,3);(5,2);(6,1);(7,0)\}$\\

Next the constraint \ref{con2} was applied to temp1:\\
$temp2=\{(0,7);(1,6);(2,5);(3,4);(4,3);(5,2);\}$\\

Again the next constraint (contraint \ref{con4}) was applied:\\
$temp3=\{(5,2)\}$\\

Last but not least the last constraint (4) is checked and the remaining tuple from the last step is valid:\\
$r=\{(5,2)\}$\\

So the final result for the Algorithm with s=t=1 is the Dupel: (5,2).\\

\subsection*{How to make unsolveable?}
To get a not solveable algorithm for example the following constraint could be added:
	\begin{equation}\\
		x_1+x_2\ge 7
	\end{equation}

Generally a new constraint just needs to be a contradiction to another constraint.

@@

One way to get an infinite solution could be to generate a endless loop with values for s and t like:
\begin{eqnarray*}
s=s*x_1\label{inf1}\\ 
t=t*x_2 \label{inf2}\\ 
or\\
s=t*x_2\label{inf3}\\ 
t=s*x_1 \label{inf4}\\ 
\end{eqnarray*}

Best idea of the evening:
Do not assume to only use integers!
Another variant is to define:
\begin{eqnarray*}
	s=\frac{1}{x_1}\\
	t=\frac{1}{x_2}\\ 
\end{eqnarray*}
the result for Z now is 2 and there are infinite many possibilities to get to 2.

\subsection*{how to get the points? ?}

P1=(0,3)
P2=(2,4)
P3=(1,3)
P4=(6,0)

>>>>

\subsection*{solution if t=s=1}
Generally we only used integers in this task. The constraint for the algorithm are as following if t and s value is 1 now:

@@

\noindent the next step we started to compute each line of the tuple. Starting with constraint \ref{con3} under the aspect of constraint \ref{con5}. All possible tuples respectively to both constraints from the assignment are:\\
$temp1=\{(0,7);(1,6);(2,5);(3,4);(4,3);(5,2);(6,1);(7,0)\}$\\

\noindent the constraint \ref{con2} was applied to temp1:\\
$temp2=\{(0,7);(1,6);(2,5);(3,4);(4,3);(5,2);\}$\\

\noindent the next constraint (constraint \ref{con4}) was applied:\\
$temp3=\{(5,2)\}$\\

\noindent but not least the last constraint (4) is checked and the remaining tuple from the last step is valid:\\
$r=\{(5,2)\}$\\

\noindent the final result for the Algorithm with s=t=1 is the tuple: (5,2). Solving the formula with this numbers 
leads us to the following maximal value: $1*x_1 + 1*x_2 = 5+2 = 7$\\

\subsection*{How to make unsolvable?}
To get a not solvable algorithm for example the following constraint could be added:
	\begin{equation}\\
		x_1+x_2\ge 7
	\end{equation}

\noindent a new constraint just needs to be a contradiction to another constraint.

@@

\noindent way to get an infinite solution could be to generate a endless loop with values for s and t like:
\begin{eqnarray*}
s=s*x_1\label{inf1}\\ 
t=t*x_2 \label{inf2}\\ 
or\\
s=t*x_2\label{inf3}\\ 
t=s*x_1 \label{inf4}\\ 
\end{eqnarray*}

\noindent idea of the evening:
Do not assume to only use integers!
Another variant is to define:
\begin{eqnarray*}
	s=\frac{1}{x_1}\\
	t=\frac{1}{x_2}\\ 
\end{eqnarray*}
the result for Z now is 2 and there are infinite many possibilities to get to 2.

\subsection*{how to get the points?}

P1=(0,3)\\
P2=(2,4)\\
P3=(1,3)\\
P4=(6,0)
